support

### 2023-04-05 analyses/CopyOfoptimizeSupport.Rmd
File Changes

---
title: "iterSim"
output: html_document
params:
  epo: 200
  patience: 5
  iteration: 2
  layer1: 12
  layer2: 12
  layer3: 100
  layer4: 100
  drpt: 0.1
  lr: 0.01
---

```{r}
library(reticulate)

@@

```{r setup, include=T}
set.seed(1)
knitr::opts_chunk$set(echo = TRUE)
source("src/packages.R")
source("src/functions.R")
library(reticulate)
eval_support<-T
#source_python('src/getSUP.py')
source_python("src/cIndex.py")
#source_python("src/dsmScript.py")
#source_python('src/deephitter.py')
##########################
###Shared Hyperparameters
##########################
#bsize=512
min_delta =0# 10^-7

@@

numSamp<-2000

baselineTrials<-2

@@

```{r complexPrep,eval=T}

##############################
###set up complex simulation
##############################

# Define a function returning the log cum hazard at time t
logcumhaz <- function(t, x, betas, knots) {

  # Obtain the basis terms for the spline-based log
  # cumulative hazard (evaluated at time t)
  basis <- flexsurv::basis(knots, log(t))

  # Evaluate the log cumulative hazard under the
  # Royston and Parmar specification
  res <-betas[["gamma0"]] * basis[[1]] + 
    betas[["gamma1"]] * basis[[2]] +
    betas[["gamma2"]] * basis[[3]] +
    betas[["gamma3"]] * basis[[4]] +
    betas[["gamma4"]] * basis[[5]] +
    betas[["z1"]] * x[["z1"]]+
    betas[["z2"]] * x[["z2"]]+
    betas[["z3"]] * x[["z3"]]+
    betas[["term1"]] * x[["z1"]]*t+#*x[["z2"]]*
    #betas[["term2"]] * x[["z1"]]*x[["z3"]]+
    betas[["term3"]] * x[["z2"]]*(x[["z3"]])
  #
  # Return the log cumulative hazard at time t
  res
}
url<-'app.txt'
ds <- read.table(url, sep = '',header = TRUE)
ds$years.at.risk=pmin(ds$agein80,ds$onset)
brcancer$rectime<-brcancer$rectime/max(brcancer$rectime)
true_mod <- flexsurv::flexsurvspline(Surv(rectime, censrec) ~ 1, data = brcancer, k = 3) #from flexsurv

# Simulate the event times
coefficients<-true_mod$coefficients
coefficients<-c(coefficients,z1=0.05,z2=1.05,z3=1.05,term1=2.4,term3=1.05)#term2=1.05,

#########################
###Simulate data
#########################
cov<-data.frame(id=1:numSamp,
                z1=c(rep(1,numSamp/2),rep(0,numSamp/2)),
                z2=c(rnorm(numSamp/2,10,0.5),rnorm(numSamp/2,0,0.5)),
                z3=c(rnorm(numSamp/2,0,0.5),rnorm(numSamp/2,10,0.5)))
true_mod <- flexsurv::flexsurvspline(Surv(rectime, censrec) ~ 1,
                                     data = brcancer, k = 3
) #from flexsurv

dat <- simsurv(betas = coefficients, # "true" parameter values
               x = cov,                   # covariate data for 200 individuals
               knots = true_mod$knots,    # knot locations for splines
               logcumhazard = logcumhaz,  # definition of log cum hazard
               maxt = 25,               # no right-censoring
               interval = c(0,10000000)) # interval for root finding
colnames(dat)<-c("id","time","status")
samp<-sample(seq(1,nrow(dat),by=1), floor(nrow(dat)*(0.1))) #random censoring
dat$status[samp]<-0
# Merge the simulated event times onto covariate data frame
data <- merge(cov, dat)
covs<-colnames(data)
data<-data[,-1]

toDiv<-max(data$time)
data$time<-data$time/toDiv
spec = c(train = .85, test = .15)

@@

res = split(data, g)
saveRDS(res$test,"ComplexSimTest.rds")

k=5
klist<-list()
data<-res$train
for(i in 1:k){

@@

  g = sample(cut(
    seq(nrow(data)), 
    nrow(data)*cumsum(c(0,spec)),
    labels = names(spec)
  ))
  klist[[i]]= split(data, g)
}
saveRDS(klist,"ComplexSimCV.rds")

@@

klist<-readRDS("ComplexSimCV.rds")
# lr=c(0.001,0.01)
# drpt=c(0.25,0.5)
# layer1=c(50,75,100)
# layer2=c(50,75)
# bsize=c(floor(nrow(klist[[1]]$train)/100))
# actv=c("relu","tanh")
# alp=c(0,0.5,1)

lr=c(0.001,0.0001)
drpt=c(.1,.2)
layer1=c(10,25,50)
layer2=c(10,20,30)
bsize=c(floor(nrow(klist[[1]]$train)/100))
actv=c("relu","tanh")
alp=c(0,0.5,1)

@@

      train<-data$train
      val<-data$val

      sds<-sapply(train, function(x) (sd(x)))
      means<-sapply(train, function(x) (mean(x)))
      val<-normalizer(val,means,sds)
      train<-normalizer(train,means,sds)

@@

      currentTime<-Sys.time() 
      coxnnsurv=fitDeepSurv(train,val,floor(nrow(train)/100),epochs=epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lr=lr,actv=actv)
      tempVal<-append(tempVal,min(coxnnsurv$val_metrics$scores$loss$score))
      runTime<-append(runTime, Sys.time()-currentTime)
      currentTime<-Sys.time()

@@

klist<-readRDS("ComplexSimCV.rds")
test<-readRDS("ComplexSimTest.rds")
times<-seq(from=min(test$time)+0.000001,
           to=max(test$time)-0.000001,
           length.out = 25
)

bestDS<-optimDeepSurv(klist,test,times,baselineTrials=baselineTrials,lr,drpt,layer1,layer2,bsize,actv)
```

```{r optimDeepHit,eval=T}

@@

      currentTime<-Sys.time() 
      hitnnSurv=fitDeephit(train,val,floor(nrow(train)/100),epochs=epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lr=lr,actv=actv,alp=alp)
      tempVal<-append(tempVal,min(hitnnSurv$val_metrics$scores$loss$score))
      runTime<-append(runTime, Sys.time()-currentTime)
      currentTime<-Sys.time() 
    }
    rm(fitDeephit)

@@

klist<-readRDS("ComplexSimCV.rds")
test<-readRDS("ComplexSimTest.rds")
times<-seq(from=min(test$time)+0.000001,
           to=max(test$time)-0.000001,
           length.out = 25
)

@@

```{r hyperopcbnn,eval=T}

optimCBNN<-function(klist,test,times,lr,drpt,layer1,layer2,bsize,actv){

@@

  paramTrials<-as.data.frame(tidyr::crossing(lr=lr,
                                             drpt=drpt,
                                             layer1=layer1,
                                             layer2=layer2,
                                             #bsize=,
                                             actv=actv,
                                             #IPA=NA,
                                             #IPAse=NA,
                                             valLoss=NA,
                                             runtime=NA))

@@

      train<-data$train
      val<-data$val

      sds<-sapply(train, function(x) (sd(x)))
      means<-sapply(train, function(x) (mean(x)))
      #val[[1]][[1]]<-as.matrix(normalizer(as.data.frame(val[[1]][[1]]),means,sds))
      train<-normalizer(train,means,sds)
      #train[,ncol(train)]<-data$train[,ncol(train)]
      val<-normalizer(val,means,sds)
      train<-sampleCaseBase(data = as.data.frame(train),time="time",event="status",ratio=100)
      valcb<-sampleCaseBase(data = as.data.frame(val),time="time",event="status",ratio=100)
      val<-list(list(as.matrix(valcb[,-c(ncol(valcb)-1,ncol(valcb))]),
                     as.matrix(valcb[,ncol(valcb),drop=F])
      ),
      as.matrix(valcb[,ncol(valcb)-1,drop=F])
      )
      val[[1]][[2]]<-rep(train$offset[1],nrow(val[[1]][[1]]))

      lr=paramTrials[i,]$lr
      drpt=paramTrials[i,]$drpt
      layer1=paramTrials[i,]$layer1
      layer2=paramTrials[i,]$layer2
      bsize=c(floor(nrow(train)/100))
      actv=paramTrials[i,]$actv

@@

      fit<-fitSmoothHaz(cbnn,
                        epochs=epo,
                        batch_size=bsize,
                        verbose=0,
                        monitor="val_loss",
                        #val_split=0.2,
                        min_delta=min_delta,
                        patience=patience,val=val)
      tempVal<-append(tempVal,min(fit$resultOfFit$metrics$val_loss))
      runTime<-append(runTime, Sys.time()-currentTime)
      currentTime<-Sys.time()

@@

klist<-readRDS("ComplexSimCV.rds")
test<-readRDS("ComplexSimTest.rds")

cbnnPerformance<-optimCBNN(klist,test,times,lr,drpt,layer1,layer2,bsize,actv)
#cbnnPerformance<-cbnnPerformance[which.min(cbnnPerformance$valLoss),]

@@

winners<-readRDS("complexOptimWins.rds")

klist<-readRDS("ComplexSimCV.rds")
data<-rbind(klist[[1]]$train,klist[[1]]$val)

@@

  val<-res$validate

  sds<-sapply(train, function(x) (sd(x)))
  means<-sapply(train, function(x) (mean(x)))

  fullTest<-readRDS("ComplexSimTest.rds")
  test<-fullTest[,-c(ncol(data))]
  test<-normalizer(fullTest,means,sds)[,-c(ncol(data))]
  fullTest<-normalizer(fullTest,means,sds)

  val<-normalizer(res$validate,means,sds)

  train<-normalizer(train,means,sds)
  valcb<-sampleCaseBase(data = as.data.frame(val),time="time",event="status",ratio=100)#rbind(train,val)
  valcb$offset<-0
  valcbtensor<-list(list(as.matrix(valcb[,-c(ncol(valcb)-1,ncol(valcb))]),as.matrix(valcb[,ncol(valcb),drop=F])),as.matrix(valcb[,ncol(valcb)-1,drop=F]))
  times<-seq(from=min(test$time)+0.000001,
             to=max(test$time)-0.000001,
             length.out = 27
  )

@@

  ###########################
  ###casebase optimal model
  ###########################
  final_mod_cb_glm <- fitSmoothHazard(status~bs(time)-time+z1+z2+z3+z1:time+z2:z3,#+z1:z3
                                      data = train,
                                      time = "time",
                                      event="status",
                                      ratio = 100
  )

  summary(final_mod_cb_glm)
  tglmAbsRisk<-absoluteRisk(final_mod_cb_glm,time=times,newdata=test,type="CI")
  tglmAbsRisk<-as.data.frame(tglmAbsRisk)
  rownames(tglmAbsRisk)<-tglmAbsRisk$time
  trueGlmProper<- t(tglmAbsRisk[-1,-1])
  class(trueGlmProper)<-c("tunnel",class(trueGlmProper))

  #########################
  ###casebase+splines
  ##########################
  mod_cb_glm <- fitSmoothHazard(status~bs(time)+.-time,
                                data = train,
                                time = "time",
                                event="status",
                                ratio = 100
  )

@@

@@

  ############################
  ###coxph
  ############################  
  cox<-coxph(Surv(time, status) ~ ., data = train,x=T)

  #############################
  ###CBNN
  #############################
  train<-sampleCaseBase(data = as.data.frame(train),time="time",event="status",ratio=100)
  valcb<-sampleCaseBase(data = as.data.frame(val),time="time",event="status",ratio=100)
  val<-list(list(as.matrix(valcb[,-c(ncol(valcb)-1,ncol(valcb))]),
                 as.matrix(valcb[,ncol(valcb),drop=F])),
            as.matrix(valcb[,ncol(valcb)-1,drop=F]))

  val[[1]][[2]]<-rep(train$offset[1],nrow(val[[1]][[1]]))   
  lr=winners$cbnn$lr
  drpt=winners$cbnn$drpt
  layer1=winners$cbnn$layer1
  layer2=winners$cbnn$layer2
  #bsize=winners$cbnn$bsize
  actv=winners$cbnn$actv

  # lr=0.001
  # drpt=0.1
  # layer1=50
  # layer2=20
  # #bsize=winners$cbnn$bsize
  # actv='relu'

  currentTime<-Sys.time() 
  # valcbtensor[[1]][[2]]<-rep(mod_cb_glm$offset[1],nrow(valcbtensor[[1]][[1]]))
  covars_input<-layer_input(shape=c(length(colnames(mod_cb_glm$data))-2),
                            name = 'main_input')

@@

  fit<-fitSmoothHaz(cbnn,
                    epochs=epo,
                    batch_size=c(floor(nrow(train)/100)),
                    verbose=0,
                    monitor="val_loss",
                    #val_split=0.2,
                    min_delta=min_delta,
                    patience=patience,val=val)
  annPreds<-aar(fit,
                times=times,
                x_test=test
  )

  rownames(annPreds)<-annPreds[,1]
  annProperpoly<- t(annPreds[,-1])
  class(annProperpoly)<-c("tunnel",class(annProperpoly)) 
  rm(fit,cbnn,covars_input,covars_output)
  ############################
  ###Brier Score
  ############################  
  brierFinalResults <- Score(list("Cox_Lin" = cox,'CB_Logi'=glmProper,
                                  'DeepSurv'=cnnCleaned,'DeepHit'=deephitCleaned,
                                  'CBNN_Poly'=annProperpoly,'optimal'=trueGlmProper),
                             data =fullTest, 
                             formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                             se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)
  BrierIPAList[[pos]]<-brierFinalResults$Brier$score

  #######################
  ###Cox 
  ######################
  a<-survfit(cox, newdata=fullTest,times=times)
  rownames(a$surv)<-a$time
  coxlinSurv<-pyProcess(t(a$surv),times=times)
  colnames(coxlinSurv)<-seq(0,1,length.out = ncol(coxlinSurv))

@@

  riskList<-list(coxlinSurv,
                 glmProper,
                 cnnCleaned,
                 deephitCleaned,
                 annProperpoly,
                 trueGlmProper
  )

  tempTims<-   as.numeric(colnames(annProperpoly))
  tempTims<-head(tempTims, -1)
  tempTims<-tail(tempTims, -1)
  cScoreTemp<-matrix(NA,nrow=length(tempTims),ncol=length(riskList)+1)
  et_train<-as.matrix(train)[,c(5,4)]
  et_test<-as.matrix(fullTest[,c(5,4)])
  colnames(cScoreTemp)<-c('times', "Cox_Lin",'CB_Logi','DeepSurv','DeepHit',
                          'cbnn','optimal')
  cScoreTemp[,1]<- tempTims

  cScore[[pos]]<-cIndexSummary(et_train=et_train,
                               et_test=et_test,
                               riskList=riskList,
                               cScore=cScoreTemp
  )

  saveRDS(BrierIPAList,'results/100complexBrier.rds')
  saveRDS(cScore,'results/100complexcidx.rds')
  pos=pos+1

@@

```{r plotComplex}

BrierIPAList<-readRDS('results/100complexBrier.rds')

@@

#end_time-start_time
ipa+coord_cartesian(ylim=c(-2,1))

@@

```{r optimDSM,eval=F}
klist<-readRDS("ComplexSimCV.rds")
test<-readRDS("ComplexSimTest.rds")
times<-seq(from=min(test$time)+0.000001,
           to=max(test$time)-0.000001,
           length.out = 25
)

paramTrials<-as.data.frame(tidyr::crossing(lr=c(0.001,0.01,0.1),
                                           drpt=c(0.25),
                                           layer1=c(10,25,50,100),
                                           layer2=c(10,25,50,100),
                                           bsize=c(floor(nrow(klist[[1]]$train)/100)),
                                           actv=c("relu","tanh"),
                                           alp=c(0,0.5,1),
                                           k=c(3,6,9),
                                           dist=c('weibull','lognormal'),
                                           #IPA=NA,
                                           #IPAse=NA,
                                           valLoss=NA,
                                           runtime=NA))

paramTrials<-paramTrials[sample(nrow(paramTrials), baselineTrials), ]

    train<-data$train
    val<-data$val

    lr=paramTrials[i,]$lr
    drpt=paramTrials[i,]$drpt
    layer1=paramTrials[i,]$layer1
    layer2=paramTrials[i,]$layer2
    bsize=paramTrials[i,]$bsize
    actv=paramTrials[i,]$actv
    alp=paramTrials[i,]$alp
    k=paramTrials[i,]$k
    dist=paramTrials[i,]$dist
    #=paramTrials[i,]$IPA
    #=paramTrials[i,]$valLoss

    source_python('src/optimDSM.py')
    dsmSurv<-dsmfitter(train,test,bsize,20,val,times,lr,actv,k,dist,layer1,layer2,tPos=3,ePos=4)
    if((sum(is.na(dsmSurv))==ncol(dsmSurv)*nrow(dsmSurv))){

      dsmSurv<-dsmfitter(train=train,fullTest=test,bsize=floor(nrow(train)/100),epochs=20,val=val,times=times,lr=lr,actv=actv,k,dist,layer1,layer2,tPos=3,ePos=4)
      py_run_string("del dsmfitter")
      rm(dsmfitter)
      next
    }
    tempVal<-append(tempVal,min(hitnnSurv$val_metrics$scores$loss$score))
    runTime<-append(runTime, Sys.time()-currentTime)
    currentTime<-Sys.time() 
  }
  rm(fitDeephit)

  #paramTrials$IPA[i]<-mean(tempRes)
  #paramTrials$IPAse[i]<-sd(tempRes)
  paramTrials$valLoss[i]<-mean(tempVal)
  paramTrials$runtime[i]<-mean(runTime)
  #saveRDS(paramTrials,"complexds.rds")
  print(paste("trial",i))
  print(mean(runTime))
  #print(as.character(paramTrials[i,]))
  #rm(cbnn,fit,annPreds,covars_input,covars_output)
  gc()
}

>>>>

---
title: "support"
output: html_document
params:
  epo: 2000
  patience: 10
  iteration: 10
  layer1: 12
  layer2: 12
  layer3: 100
  layer4: 100
  drpt: 0.1
  lr: 0.01
---

library(reticulate)
```

@@

```{r setup, include=T}
set.seed(1234)
knitr::opts_chunk$set(echo = TRUE)
source("src/packages.R")
source("src/functions.R")
eval_support<-T
#source_python('src/getSUP.py')
source_python("src/cIndex.py")
#source_python("src/dsmScript.py")
#source_python('src/deephitter.py')
##########################
###Shared Hyperparameters
##########################
#bsize=512
min_delta = 0# 10^-7

@@

baselineTrials<-5

@@

```{r supPrep,eval=T}

source_python('src/getSUP.py')
data<- as.data.frame(do.call(cbind, getSupportPycox()))

colnames(data)[ncol(data)-1]<-'time'
colnames(data)[ncol(data)]<-'status'

data<-data[-which(data$x2 %in% c(8,9)),]

for(i in c(2,3,4,5,6,7)){#3,4,
  data[, i]<-as.factor(data[, i])
}
data<-as.data.frame(model.matrix(~.,data)[,-1])
#data<-as.data.frame(sapply(data, function(x) (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm=T))))

covs<-colnames(data)
names(data)[seq(1,length(covs)-2)] <- paste("z", seq(1,length(covs)-2), sep="")

names(data)[ncol(data)-1]<-"time"
names(data)[ncol(data)]<-"status"

covs<-colnames(data)

#toDiv<-max(data$time)
#data$time<-data$time/toDiv
#data$time<-data$time/max(data$time)
spec = c(train = .85, test = .15)

@@

res = split(data, g)
saveRDS(res$test,"supportTest.rds")

k=3
klist<-list()
data<-res$train
for(i in 1:k){

@@

  g = sample(cut(
    seq(nrow(data)), 
    nrow(data)*cumsum(c(0,spec)),
    labels = names(spec)
  ))
  klist[[i]]= split(data, g)
}
saveRDS(klist,"supportCV.rds")

@@

klist<-readRDS("supportCV.rds")

lr=c(0.001)
drpt=c(0.25,0.5)
layer1=c(10,20,30)
layer2=c(10,20,30)
bsize=c(floor(nrow(klist[[1]]$train)/100))
actv=c("relu","linear")#,"tanh"
alp=c(0)

@@

      train<-data$train
      val<-data$val
      maxTime<-max(train$time)
      sds<-sapply(train, function(x) (sd(x)))
      means<-sapply(train, function(x) (mean(x)))
      val<-normalizer(val,means,sds,maxTime)
      train<-normalizer(train,means,sds,maxTime)

@@

      currentTime<-Sys.time() 
      coxnnsurv=fitDeepSurv(train,val,bsize,epochs=epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lr=lr,actv=actv)
      #tempVal<-append(tempVal,min(coxnnsurv$val_metrics$scores$loss$score))
      scores<-na.omit(coxnnsurv$val_metrics$scores$loss$score)

      tempVal<-append(tempVal,scores[length(scores)])
      runTime<-append(runTime, Sys.time()-currentTime)
      currentTime<-Sys.time()

@@

klist<-readRDS("supportCV.rds")
test<-readRDS("supportTest.rds")
times<-seq(from=min(test$time)+0.000001,
           to=max(test$time)-0.000001,
           length.out = 25
)

bestDS<-optimDeepSurv(klist,test,times,baselineTrials=baselineTrials,lr,drpt,layer1,layer2,bsize,actv)

```{r optimDeepHit,eval=reoptimize}

@@

      currentTime<-Sys.time() 
      hitnnSurv=fitDeephit(train,val,bsize,epochs=epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lr=lr,actv=actv,alp=alp)
      #tempVal<-append(tempVal,min(hitnnSurv$val_metrics$scores$loss$score))
      scores<-na.omit(hitnnSurv$val_metrics$scores$loss$score)

      tempVal<-append(tempVal,scores[length(scores)])
      runTime<-append(runTime, Sys.time()-currentTime)
      currentTime<-Sys.time() 
    }
    rm(fitDeephit)

@@

klist<-readRDS("supportCV.rds")
test<-readRDS("supportTest.rds")
times<-seq(from=min(test$time)+0.000001,
           to=max(test$time)-0.000001,
           length.out = 25
)

@@

```{r hyperopcbnn,eval=reoptimize}

optimCBNN<-function(klist,test,times,lr,drpt,layer1,layer2,nBatch,actv){

@@

  paramTrials<-as.data.frame(tidyr::crossing(lr=lr,
                                             drpt=drpt,
                                             layer1=layer1,
                                             layer2=layer2,
                                             nBatch=nBatch,
                                             actv=actv,
                                             #IPA=NA,
                                             #IPAse=NA,
                                             valLoss=NA,
                                             runtime=NA))

@@

      train<-data$train
      val<-data$val
      maxTime<-max(train$time)
      sds<-sapply(train, function(x) (sd(x)))
      means<-sapply(train, function(x) (mean(x)))
      #val[[1]][[1]]<-as.matrix(normalizer(as.data.frame(val[[1]][[1]]),means,sds))
      train<-normalizer(train,means,sds,1)

      #train[,ncol(train)]<-data$train[,ncol(train)]
      val<-normalizer(val,means,sds,1)
      train<-sampleCaseBase(data = as.data.frame(train),time="time",event="status",ratio=100)
      valcb<-sampleCaseBase(data = as.data.frame(val),time="time",event="status",ratio=100)
      val<-list(list(as.matrix(valcb[,-c(ncol(valcb)-1,ncol(valcb))]),
                     as.matrix(valcb[,ncol(valcb),drop=F])
      ),
      as.matrix(valcb[,ncol(valcb)-1,drop=F])
      )
      val[[1]][[2]]<-rep(train$offset[1],nrow(val[[1]][[1]]))
      #val[[1]][[2]]<-rep(0,nrow(val[[1]][[1]]))

      lr=paramTrials[i,]$lr
      drpt=paramTrials[i,]$drpt
      layer1=paramTrials[i,]$layer1
      layer2=paramTrials[i,]$layer2
      bsize=c(floor(nrow(train)/paramTrials[i,]$nBatch))
      actv=paramTrials[i,]$actv

@@

      fit<-fitSmoothHaz(cbnn,
                        epochs=epo,
                        batch_size=bsize,
                        verbose=0,
                        monitor="val_loss",
                        #val_split=0.2,
                        min_delta=min_delta,
                        patience=patience,val=val)
      #tempVal<-append(tempVal,min(fit$resultOfFit$metrics$val_loss))

      scores<-na.omit(fit$resultOfFit$metrics$val_loss)

      tempVal<-append(tempVal,scores[length(scores)])
      runTime<-append(runTime, Sys.time()-currentTime)
      currentTime<-Sys.time()

@@

klist<-readRDS("supportCV.rds")
test<-readRDS("supportTest.rds")

cbnnPerformance<-optimCBNN(klist,test,times,lr,drpt,layer1,layer2,bsize,actv)
#cbnnPerformance<-cbnnPerformance[which.min(cbnnPerformance$valLoss),]
```

```{r winners}
winners<-list(cbnn=cbnnPerformance,
              ds=bestDS,
              dh=bestDH)

saveRDS(winners,"supportWins.rds")

@@

winners<-readRDS("supportWins.rds")

klist<-readRDS("supportCV.rds")
data<-rbind(klist[[1]]$train,klist[[1]]$val)
#data$time<-data$time/max(data$time)

@@

  #train<-res$train
  val<-res$validate

  sds<-sapply(train, function(x) (sd(x)))
  means<-sapply(train, function(x) (mean(x)))
  maxTime<-max(train$time)

  fullTest<-readRDS("supportTest.rds")
  test<-fullTest[,-c(ncol(data))]
  test<-normalizer(fullTest,means,sds,maxTime)[,-c(ncol(data))]
  fullTest<-normalizer(fullTest,means,sds,maxTime)

  val<-normalizer(res$validate,means,sds,maxTime)

  train<-normalizer(train,means,sds,maxTime)

  linModelTrain<-as.data.frame(rbind(train,val))
  #valcb<-sampleCaseBase(data = as.data.frame(val),time="time",event="status",ratio=100)#rbind(train,val)
  #valcb$offset<-0
  #valcbtensor<-list(list(as.matrix(valcb[,-c(ncol(valcb)-1,ncol(valcb))]),as.matrix(valcb[,ncol(valcb),drop=F])),as.matrix(valcb[,ncol(valcb)-1,drop=F]))
  times<-seq(from=min(test$time),
             to=max(test$time),
             length.out = 22
  )

@@

  #########################
  ###casebase+splines
  ##########################
  mod_cb_glm <- casebase::fitSmoothHazard(status~bs(time)+.-time,
                                data = linModelTrain,
                                time = "time",
                                event= "status",
                                ratio = 100
  )

@@

    miniee <- Score(list('mod'=cnnCleaned),
                             data =fullTest, 
                             formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                             se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)$Brier$score
   miniee$IBS[which(miniee$model=="mod" & miniee$times==max(miniee$times))]

@@

  ############################
  ###coxph
  ############################  
  cox<-coxph(Surv(time, status) ~ ., data = linModelTrain,x=T)

  #############################
  ###CBNN
  #############################
  tempTrain<-train
  train<-sampleCaseBase(data = as.data.frame(train),time="time",event="status",ratio=100)
  valcb<-sampleCaseBase(data = as.data.frame(val),time="time",event="status",ratio=100)
  val<-list(list(as.matrix(valcb[,-c(ncol(valcb)-1,ncol(valcb))]),
                 as.matrix(valcb[,ncol(valcb),drop=F])),
            as.matrix(valcb[,ncol(valcb)-1,drop=F]))

  val[[1]][[2]]<-rep(train$offset[1],nrow(val[[1]][[1]]))   
  lr=winners$cbnn$lr
  drpt=winners$cbnn$drpt
  layer1=winners$cbnn$layer1
  layer2=winners$cbnn$layer2
  bsize=c(floor(nrow(train)/winners$cbnn$nBatch))
  actv=winners$cbnn$actv
   # 
   # 
   #  lr=0.001
   #  drpt=0.5
   #  layer1=10
   #  layer2=10
   #  patience=10
    actv='linear'

  currentTime<-Sys.time() 
  covars_input<-layer_input(shape=c(length(colnames(mod_cb_glm$data))-2),
                            name = 'main_input')

  covars_output<-covars_input%>%
    layer_dense(units=layer1,use_bias = T)%>%
    layer_activation(activation = actv)%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer2,use_bias = T)%>%
    layer_activation(activation = actv)%>%
    layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)

@@

  fit<-fitSmoothHaz(cbnn,
                    epochs=epo,
                    batch_size=bsize,
                    verbose=0,
                    monitor="val_loss",
                    #val_split=0.2,
                    min_delta=min_delta,
                    patience=patience,val=val)
  annPreds<-aar(fit,
                times=times,
                x_test=test
  )

  rownames(annPreds)<-annPreds[,1]
  annProperpoly<- t(annPreds[,-1])
  class(annProperpoly)<-c("tunnel",class(annProperpoly))

  ############################
  ###Brier Score
  ############################  
  brierFinalResults <- Score(list("Cox_Lin" = cox,'CB_Logi'=glmProper,
                                  'DeepSurv'=cnnCleaned,'DeepHit'=deephitCleaned,
                                  'CBNN_Poly'=annProperpoly),
                             data =fullTest, 
                             formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                             se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)
  BrierIPAList[[pos]]<-brierFinalResults$Brier$score

  ggplot(data=brierFinalResults$Brier$score, aes(x=times,y=IPA,col=model))+
    geom_line()#+coord_cartesian(ylim=c(-0.1,0.2))
  rm(fit,cbnn,covars_input,covars_output)
  #######################
  ###Cox 
  ######################
  a<-survfit(cox, newdata=fullTest,times=times)
  rownames(a$surv)<-a$time
  coxlinSurv<-pyProcess(t(a$surv),times=times)
  colnames(coxlinSurv)<-seq(0,1,length.out = ncol(coxlinSurv))

@@

  riskList<-list(coxlinSurv,
                 glmProper,
                 cnnCleaned,
                 deephitCleaned,
                 annProperpoly
  )

  tempTims<-   as.numeric(colnames(annProperpoly))
  tempTims<-head(tempTims, -1)
  tempTims<-tail(tempTims, -1)
  cScoreTemp<-matrix(NA,nrow=length(tempTims),ncol=length(riskList)+1)
  et_train<-as.matrix(tempTrain)[,c(ncol(tempTrain),ncol(tempTrain)-1)]
  et_test<-as.matrix(fullTest[,c(ncol(fullTest),ncol(fullTest)-1)])
  colnames(cScoreTemp)<-c('times', "Cox_Lin",'CB_Logi','DeepSurv','DeepHit',
                          'cbnn')
  cScoreTemp[,1]<- tempTims

  cScore[[pos]]<-cIndexSummary(et_train=et_train,
                               et_test=et_test,
                               riskList=riskList,
                               cScore=cScoreTemp
  )
  print(paste("current iter:",pos))
  saveRDS(BrierIPAList,'results/100supportBrier.rds')
  saveRDS(cScore,'results/100supportcidx.rds')
  pos=pos+1

@@

```{r plotsupport}

BrierIPAList<-readRDS('results/100supportBrier.rds')

@@

ipa+coord_cartesian(ylim=c(-0.1,0.2))
#end_time-start_time

@@
